Language and vision in conceptual processing: Multilevel analysis and statistical power

### 2022-10-23 manuscript/appendix-B-frequentist-analysis-diagnostics.Rmd
23102022

The residuals of the linear mixed-effects models in the three studies violated the assumption of normality. Even though linear mixed-effects models tend to be quite robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020], we sought to verify our results. To this end, two robust models were performed in each study, as described below.

@@

The first method uses the R package 'robustlmm' v2.4-4 [@R-robustlmm]. To calculate the p values, we followed the procedure of @sleegersPupillometryHindsightBias2021, but used the Kenward-Roger method instead of Satterthwaite [see @luke2017a].

@@

We followed a method proposed by @loTransformNotTransform2015, based on generalized linear mixed-effects models (GLMM) implementing an identity link function. According to @loTransformNotTransform2015, the link function helps avoid directly transforming the dependent variable, which can hinder the interpretability of the results [also see @kniefViolatingNormalityAssumption2021].

@@

*P* values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models [@luke2017a; @R-afex].

Neither Method A nor Method B could finally be used, as the code produced errors. These errors are shown in the corresponding scripts inside the 'model_diagnostics' folder in each study. Nonetheless, the residuals are shown below.

>>>>

The residuals of the linear mixed-effects models in the three studies violated the assumption of normality. Even though linear mixed-effects models tend to be quite robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020], we sought to verify our results. To this end, we attempted to run robust models using two methods, neither of which worked. The methods are nonetheless described below.

@@

The first method drew on the R package 'robustlmm' v2.4-4 [@R-robustlmm]. To calculate the $p$ values, we followed the procedure of @sleegersPupillometryHindsightBias2021, but used the Kenward-Roger method instead of Satterthwaite [see @luke2017a].

@@

In the second approach, we followed a method proposed by @loTransformNotTransform2015, based on generalized linear mixed-effects models (GLMM) implementing an identity link function. According to @loTransformNotTransform2015, the link function helps avoid directly transforming the dependent variable, which can hinder the interpretability of the results [also see @kniefViolatingNormalityAssumption2021].

@@

$P$ values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models [@luke2017a; @R-afex].

Neither Method A nor Method B could finally be used, as the code produced errors. These errors are shown in the corresponding scripts inside the 'model_diagnostics' folder in each study.

The residuals of the final models are shown in the corresponding sections below.

### 2022-10-23 manuscript/manuscript.tex
23102022

The residuals of the linear mixed-effects models in the three studies violated the assumption of normality. Even though linear mixed-effects models tend to be quite robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020), we sought to verify our results. To this end, two robust models were performed in each study, as described below.

@@

The first method uses the R package `robustlmm' v2.4-4 (Koller, 2016). To calculate the p values, we followed the procedure of Sleegers et al. (2021), but used the Kenward-Roger method instead of Satterthwaite (see Luke, 2017).

@@

We followed a method proposed by Lo and Andrews (2015), based on generalized linear mixed-effects models (GLMM) implementing an identity link function. According to Lo and Andrews (2015), the link function helps avoid directly transforming the dependent variable, which can hinder the interpretability of the results (also see Knief \& Forstmeier, 2021).

@@

\emph{P} values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models (Luke, 2017; Singmann et al., 2021).

Neither Method A nor Method B could finally be used, as the code produced errors. These errors are shown in the corresponding scripts inside the `model\_diagnostics' folder in each study. Nonetheless, the residuals are shown below.

>>>>

The residuals of the linear mixed-effects models in the three studies violated the assumption of normality. Even though linear mixed-effects models tend to be quite robust to deviations from normality (Knief \& Forstmeier, 2021; Schielzeth et al., 2020), we sought to verify our results. To this end, we attempted to run robust models using two methods, neither of which worked. The methods are nonetheless described below.

@@

The first method drew on the R package `robustlmm' v2.4-4 (Koller, 2016). To calculate the \(p\) values, we followed the procedure of Sleegers et al. (2021), but used the Kenward-Roger method instead of Satterthwaite (see Luke, 2017).

@@

In the second approach, we followed a method proposed by Lo and Andrews (2015), based on generalized linear mixed-effects models (GLMM) implementing an identity link function. According to Lo and Andrews (2015), the link function helps avoid directly transforming the dependent variable, which can hinder the interpretability of the results (also see Knief \& Forstmeier, 2021).

@@

\(P\) values were to be calculated through parametric bootstrapping, which is the most robust method for GLMMs, as the Kenward-Roger and Satterthwaite methods are not available for these models (Luke, 2017; Singmann et al., 2021).

Neither Method A nor Method B could finally be used, as the code produced errors. These errors are shown in the corresponding scripts inside the `model\_diagnostics' folder in each study.

The residuals of the final models are shown in the corresponding sections below.
